Why aren't significance tests commonly used for linear regression diagnostics?

### 2022-09-20 paper_comparison/paper_comparison/paper_comparison.Rmd
add Heteroskedasticity design

@@

Experiment I is designed to study the ability of human subjects to detect the effect of a random vector $\boldsymbol{z}$ which is a probabilist's Hermite polynomial [Herimite ref here] of another random vector $\boldsymbol{x}$ in a two variable statistical model formulated as:

@@

```{=tex}
\begin{equation} \label{eq:scaling-function}
g(\boldsymbol{x}, k) = (\boldsymbol{x} - min(\boldsymbol{x}))/max(\boldsymbol{x} - min(\boldsymbol{x})) \times 2k - k, \quad \text{for} \quad k > 0. 
\end{equation}
```

@@

Since $z = O(x^j)$, for $j > 1$, $z$ is a higher order term leaves out by the null regression causing model misspecification.

@@

@@

>>>>

Two types of departures were considered with the corresponding data generating process being designed for Experiment I and II.

@@

Experiment I is designed to study the ability of human subjects to detect the effect of a non-linear term $\boldsymbol{z}$ which is a probabilist's Hermite polynomial [Herimite ref here] of another random vector $\boldsymbol{x}$ in a two variable statistical model formulated as:

@@

```{=tex}
\begin{equation} \label{eq:scaling-function}
g(\boldsymbol{x}, k) = (\boldsymbol{x} - min(\boldsymbol{x}))/max(\boldsymbol{x} - min(\boldsymbol{x}))2k - k, \quad \text{for} \quad k > 0. 
\end{equation}
```

@@

Since $z = O(x^j)$, for $j > 1$, $z$ is a higher order term leaves out by the null regression, which will result in model misspecification.

@@

Experiment II is designed to study the ability of human subjects to detect the appearance of a heteroskedasticity pattern under a simple linear regression model setting:

```{=tex}
\begin{align} \label{eq:heter-model}
\boldsymbol{y} = 1 + \boldsymbol{x} + \boldsymbol{\varepsilon},\\
\boldsymbol{\varepsilon} \sim N(\boldsymbol{0}, 1 + 2 - |a| b (\boldsymbol{x} - a)^2 \boldsymbol{I}), \\
\end{align}
```
where $\boldsymbol{y}$, $\boldsymbol{x}$, $\boldsymbol{\varepsilon}$ are vector of size $n$.

The null regression model used to fit the realizations generated by the above model is formulated exactly the same as the model used in the first experiment:

```{=tex}
\begin{equation}
\boldsymbol{y} = \beta_0 + \beta_1 \boldsymbol{x} + \boldsymbol{u},
\end{equation}
```
where $\boldsymbol{u} \sim N(\boldsymbol{0}, \sigma^2\boldsymbol{I}_n)$.

For $b \neq 0$, the variance-covariance matrix of the error term $\boldsymbol{\varepsilon}$ is correlated with the regressor $x$, which will lead to the presence of heteroskedasticity.

@@

Experiment data were simulated using three different shapes ($a$ = -1, 0, 1), five different values of $b$ (b = 0.25, 1, 4, 16, 64), three different sample sizes (n = 50, 100, 300) and four different distribution of $X_{raw}$: (1) $U(-1, 1)$, (2) $N(0, 0.3^2)$, (3) $lognormal(0, 0.6^2)/3$ and (4) $u\{1, 5\}$. A summary of the parameters used in this experiment is given in Table \ref{tab:parameter-table}.

The values of $a$ was chosen so that different shapes of heteroskedasticity were included in the residual plot. These include triangle shape, butterfly shape and inverse triangle shape.

```{r different-shape-of-heter}
stand_dist <- function(x) (x - min(x))/max(x - min(x)) * 2 - 1

ori_dat <- heter_model(a = -1, x = {raw_x <- rand_uniform(-1, 1); closed_form(~stand_dist(raw_x))}, b = 128)$gen(300)

VI_MODEL$plot(ori_dat) +
  ggtitle(quote("Triangle shape")) +
  theme_light() -> p1

VI_MODEL$plot(heter_model(a = 0, x = {raw_x <- rand_uniform(-1, 1); closed_form(~stand_dist(raw_x))}, b = 128)$gen(300, computed = select(ori_dat, x, e))) +
  ggtitle(quote("Butterfly shape")) +
  theme_light() -> p2

VI_MODEL$plot(heter_model(a = 1, x = {raw_x <- rand_uniform(-1, 1); closed_form(~stand_dist(raw_x))}, b = 128)$gen(300, computed = select(ori_dat, x, e))) +
  ggtitle(quote("Inverse triangle shape")) +
  theme_light() -> p3

patchwork::wrap_plots(p1, p2, p3, ncol = 3)
```

The range of $b$, which is a factor controlling the strength of the signal, was chosen so that different difficulty levels of lineups were generated, and therefore, the estimated power curve would be smooth and continuous.

### 2022-09-20 paper_comparison/paper_comparison/paper_comparison.tex
add Heteroskedasticity design

Experiment I is designed to study the ability of human subjects to
detect the effect of a random vector \(\boldsymbol{z}\) which is a
probabilist's Hermite polynomial {[}Herimite ref here{]} of another
random vector \(\boldsymbol{x}\) in a two variable statistical model
formulated as:

@@

\begin{equation} \label{eq:scaling-function}
g(\boldsymbol{x}, k) = (\boldsymbol{x} - min(\boldsymbol{x}))/max(\boldsymbol{x} - min(\boldsymbol{x})) \times 2k - k, \quad \text{for} \quad k > 0. 
\end{equation}

@@

Since \(z = O(x^j)\), for \(j > 1\), \(z\) is a higher order term leaves
out by the null regression causing model misspecification.

@@

@@

>>>>

Experiment I is designed to study the ability of human subjects to
detect the effect of a non-linear term \(\boldsymbol{z}\) which is a
probabilist's Hermite polynomial {[}Herimite ref here{]} of another
random vector \(\boldsymbol{x}\) in a two variable statistical model
formulated as:

@@

\begin{equation} \label{eq:scaling-function}
g(\boldsymbol{x}, k) = (\boldsymbol{x} - min(\boldsymbol{x}))/max(\boldsymbol{x} - min(\boldsymbol{x}))2k - k, \quad \text{for} \quad k > 0. 
\end{equation}

@@

Since \(z = O(x^j)\), for \(j > 1\), \(z\) is a higher order term leaves
out by the null regression, which will result in model misspecification.

@@

Experiment II is designed to study the ability of human subjects to
detect the appearance of a heteroskedasticity pattern under a simple
linear regression model setting:

\begin{align} \label{eq:heter-model}
\boldsymbol{y} = 1 + \boldsymbol{x} + \boldsymbol{\varepsilon},\\
\boldsymbol{\varepsilon} \sim N(\boldsymbol{0}, 1 + 2 - |a| b (\boldsymbol{x} - a)^2 \boldsymbol{I}), \\
\end{align}

where \(\boldsymbol{y}\), \(\boldsymbol{x}\),
\(\boldsymbol{\varepsilon}\) are vector of size \(n\).

The null regression model used to fit the realizations generated by the
above model is formulated exactly the same as the model used in the
first experiment:

\begin{equation}
\boldsymbol{y} = \beta_0 + \beta_1 \boldsymbol{x} + \boldsymbol{u},
\end{equation}

For \(b \neq 0\), the variance-covariance matrix of the error term
\(\boldsymbol{\varepsilon}\) is correlated with the regressor \(x\),
which will lead to the presence of heteroskedasticity.

@@

Experiment data were simulated using three different shapes (\(a\) = -1,
0, 1), five different values of \(b\) (b = 0.25, 1, 4, 16, 64), three
different sample sizes (n = 50, 100, 300) and four different
distribution of \(X_{raw}\): (1) \(U(-1, 1)\), (2) \(N(0, 0.3^2)\), (3)
\(lognormal(0, 0.6^2)/3\) and (4) \(u\{1, 5\}\). A summary of the
parameters used in this experiment is given in Table
\ref{tab:parameter-table}.

The values of \(a\) was chosen so that different shapes of
heteroskedasticity were included in the residual plot. These include
triangle shape, butterfly shape and inverse triangle shape.

\includegraphics[width=1\linewidth]{paper_comparison_files/figure-latex/different-shape-of-heter-1}

The range of \(b\), which is a factor controlling the strength of the
signal, was chosen so that different difficulty levels of lineups were
generated, and therefore, the estimated power curve would be smooth and
continuous.
